Frequent Inspections Fail to Curb Violations in Toronto's Good-Standing Food Establishments

### 2024-09-28 paper/paper.qmd
added some comments, added sketches, organized

# Plot the adjusted graph
ggplot(inspection_infraction_data, aes(x = inspection_count, y = infraction_count)) +
  geom_point(color = "purple", size = 2, alpha = 0.7) +  # Purple dots
  geom_smooth(method = "lm", color = "darkgray", linetype = "dashed", se = FALSE) +  # Regression line
  scale_x_continuous(breaks = seq(0, 60, by = 10)) +  
  scale_y_continuous(breaks = seq(0, 60, by = 10)) +  
  labs(x = "Number of Inspections",
       y = "Number of Confirmed Infractions") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

@@

# Plot with more refined styling and complexity
ggplot(inspections_over_time, aes(x = month, y = inspections)) +
  geom_line(color = "black", size = 1.2) +  # Grayscale line for monthly inspections
  geom_point(color = "purple", size = 2, alpha = 0.8) +  # Purple points for each month
  labs(x = "Month",
       y = "Number of Inspections") +
  scale_x_date(date_labels = "%b %Y", date_breaks = "3 months") +  # Customize date labels and breaks
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),  # Center and bold title
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray40"),  # Style subtitle
    axis.title.x = element_text(size = 12, face = "bold"),  # Style x-axis label
    axis.title.y = element_text(size = 12, face = "bold"),  # Style y-axis label
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.text.y = element_text(size = 10, color = "black"),  # Style y-axis ticks
    panel.grid.major = element_line(size = 0.2, color = "gray80"),  # Lighter grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines
  )

@@

# Refined plot with purple percentage numbers
ggplot(type_percentage_comparison, aes(x = `Establishment Type`, y = percentage_with_infractions)) +
  geom_bar(stat = "identity", fill = "gray40", color = "black", width = 0.6) +  # Grayscale bar with refined styling
  geom_text(aes(label = sprintf("%.1f%%", percentage_with_infractions)), vjust = -0.5, size = 5, color = "purple") +  # Purple labels
  ylim(0, 80) +  # Increase the limit of the y-axis to give more space at the top
  labs(x = "Establishment Type",
       y = "Percentage of Inspections with Infractions (%)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),  # Center and bold title
    plot.subtitle = element_text(hjust = 0.5, size = 12, color = "gray40"),  # Style subtitle
    axis.title.x = element_text(size = 12, face = "bold"),  # Style x-axis label
    axis.title.y = element_text(size = 12, face = "bold"),  # Style y-axis label
    axis.text.x = element_text(size = 12),  # Style x-axis ticks
    axis.text.y = element_text(size = 12),  # Style y-axis ticks
    panel.grid.major = element_line(size = 0.2, color = "gray80"),  # Lighter grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines
  )

>>>>

# Plot the adjusted graph
ggplot(inspection_infraction_data, aes(x = inspection_count, y = infraction_count)) +
  geom_point(color = "purple", size = 2, alpha = 0.7) +  # Purple dots
  geom_smooth(method = "lm", color = "darkgray", linetype = "dashed", se = FALSE) +  # Regression line
  scale_x_continuous(breaks = seq(0, 60, by = 10)) +  
  scale_y_continuous(breaks = seq(0, 60, by = 10)) +  
  labs(x = "Number of Inspections",
       y = "Number of Confirmed Infractions") +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

@@

# Plot with more refined styling and complexity
ggplot(inspections_over_time, aes(x = month, y = inspections)) +
  geom_line(color = "black", size = 1.2) +  # Grayscale line for monthly inspections
  geom_point(color = "purple", size = 2, alpha = 0.8) +  # Purple points for each month
  labs(x = "Month",
       y = "Number of Inspections") +
  scale_x_date(date_labels = "%b %Y", date_breaks = "3 months") +  # Customize date labels and breaks
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12), 
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.text.y = element_text(size = 10, color = "black"),  # Style y-axis ticks
    panel.grid.major = element_line(size = 0.2, color = "gray80"),  # Lighter grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines
  )

@@

# Refined plot with purple percentage numbers
ggplot(type_percentage_comparison, aes(x = `Establishment Type`, y = percentage_with_infractions)) +
  geom_bar(stat = "identity", fill = "gray40", color = "black", width = 0.6) +  # Grayscale bar with refined styling
  geom_text(aes(label = sprintf("%.1f%%", percentage_with_infractions)), vjust = -0.5, size = 5, color = "purple") +  # Purple labels
  ylim(0, 80) +  # Increase the limit of the y-axis to give more space at the top
  labs(x = "Establishment Type",
       y = "Percentage of Inspections with Infractions (%)") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 11),  # Style x-axis label
    axis.title.y = element_text(size =11),  # Style y-axis label
    axis.text.x = element_text(size = 12),  # Style x-axis ticks
    axis.text.y = element_text(size = 12),  # Style y-axis ticks
    panel.grid.major = element_line(size = 0.2, color = "gray80"),  # Lighter grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines
  )
